Wetting of adhesive fluid controls insect adhesion in air and underwater

### 2021-02-10 source/tex/ladybug_adhesion.tex

\email{butt@mpip-mainz.mpg.de}

@@

\begin{document}
\begin{abstract}
Insects like beetles can stick to various surfaces using hairy pads
mediated by an oily adhesive fluid. It was previously shown that the
pads can even attach underwater, presumably due to an air bubble trapped
around the pad. However, the bubble's relative contribution to adhesion
via capillary force remains unclear. To investigate the exact role
of bubble, in this study, we perform\emph{ in-vivo} underwater adhesion
measurements of a ladybug's pad, in the presence and absence of the
trapped bubble and compare it with its adhesion in air. Our experiments
reveal that on a hydrophobic substrate, even without a bubble, the
pad can show adhesion underwater comparable to that in air. On a hydrophilic
substrate, underwater adhesion is significantly reduced, with or without
a trapped bubble. To explain these results, we develop a simple theoretical
model to estimate the net adhesion of a hairy pad due to capillary
forces. Our results demonstrate that the wetting properties of the
adhesive fluid determines the insect's adhesion in both air and underwater
conditions.
\end{abstract}

@@

The question of how insects can walk on smooth surfaces against gravity
has fascinated scientists for at least the past three centuries \cite{RN198,RN59}.
We now know that such animals are able to adhere by using specialized
organs on their feet called adhesive pads. These adhesive pads exist
in a variety of types depending on the animal, but are generally categorized
into: 1) ``smooth pads'' found in ants\cite{RN201}, stick insects
\cite{RN182}, etc. and 2) ``hairy pads'' seen in flies \cite{RN155},
geckos \cite{RN202} and others. The hairy pads show: 1) compliance
to rough surfaces due to their lower effective modulus, 2) angle dependent
adhesion due to asymmetric hair geometry and 3) self-cleaning capability
\cite{RN20}, which makes them suitable to adhere to most surfaces
reversibly. Many of these insects pads also secrete an adhesive fluid,
as seen in flies and ants \cite{RN201} (``wet adhesion''), while
others such as spiders and geckos rely on their dry hairy pads for
attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid
secretion can enforce adhesion through surface tension and viscous
forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van
der Waals forces \cite{RN202}.

@@

While most of the studies on insect adhesion are done under natural
conditions in air, insect attachment underwater has been relatively
unexplored. Typically, underwater adhesion is complicated to achieve
due to the difficulty in displacing the water layer and enable good
contact\cite{RN123}. Regardless, a study on leaf beetles\cite{RN87}
has revealed that they can in fact attach quite well to surfaces underwater.
Its hairy pad traps an air bubble underwater, which dewets the surface
on contact. It has been hypothesized that a combination of capillary
forces due the air bubble and hair contact within the dewetted area
results in its adhesion underwater. However, a detailed investigation
of the bubble's contribution and necessity to adhere to different
surfaces is lacking. Geckos are also known to adhere underwater, where
its shear adhesion force on hydrophobic substrates are similar in
both air and underwater conditions. Interestingly, its adhesion on
a fluorinated substrate is even larger underwater than in air\cite{RN15}.
This has been partially explained by a thermodynamic work of adhesion
model, assuming full displacement of water at the interface, leading
to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalized picture of adhesion
in insects which use hairy pads secreting a fluid for attachment.
First, we perform adhesion measurements of a single constrained pad
of a live ladybug beetle in air and underwater conditions, both on
smooth hydrophilic and hydrophobic glass surfaces, with a microscopic
observation of the contact process. Second, we develop a simple theoretical
model considering capillary forces to predict the net adhesion force
of a hairy pad under different conditions. Finally, we discuss key
insights gained from our experiments and model, as well as possible
implications in understanding adhesion in other animals.

@@

Seven-spotted adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) were used for adhesion
tests. The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water\emph{ ad libitum}.

Experiments were done on male beetles. Each leg of the beetle has
a pair of hairy pads covered with mostly discoidal shaped setae, capable
of strong adhesion. For the test, we only allowed the distal-end pad
to make contact. The beetle's leg was constrained similar to the method
described by Bullock et al \cite{RN19}. A steel ball fixed with a
piece of thick solder wire served as a rotatable holder to fix the
beetle and align its leg (Figure \ref{fig:Setup}). The beetle was
first anesthetized using CO\textsubscript{2} sublimating from a piece
of dry ice and then glued to the steel ball on its back. Its front
left leg was carefully fixed to the solder wire of the holder using
Blue-Tac. Its claws were fixed using epoxy glue to prevent any wiggling.
A small piece of non-sticky Teflon tape helped to keep its other legs
tucked close to the body and avoid their interference during the adhesion
test.

@@

The substrate wettability was characterized by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
De-ionized water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate. Static
contact angles were measured for a 5 \textgreek{m}l drop.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R} & \ensuremath{\theta}\textsubscript{S}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{} & 57\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{} & 110\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{} & 72\ensuremath{\pm}2\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Static and dynamic contact angles measurements \label{tab:Contact-Angles}}
\end{table}

@@

Field Desorption Mass Spectrometry (FDMS) measurements of the adhesive
fluid secretions were performed using ZAB 2-SE-FPD spectrometer (VG
Instruments). A previous study on archanids \cite{RN223} reported
that the secreted fluid does not dissolve away in water. To confirm
this for the beetle, measurements before and after the immersion of
its legs in water were done. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was immersed in 100
\textmu L milli-Q water for 15 min, then in THF for 20 min and then
transferred to the measurement chamber of the spectrometer. Molecular
composition was extracted from the peak positions of the FDMS data.

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A 3 axis manual micro-manipulator
together with the rotatable steel ball allowed good alignment of the
beetle's foot to the substrate. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2x objective and a stereo-microscope with 1x
objective (\emph{Wild Heerbrugg}) fit with cameras were used to record
the sample contact with the substrate from ventral and side views
respectively. Pad contact area was visualized through the substrate
in total reflection mode by the ventral view camera. The data acquisition
from the force sensor and cameras, together with the appropriate piezo
motion steps were synchronized using a custom LABVIEW program. Force
data was acquired at a sample rate of 984 Hz, averaged to 512 points
per motion step. Videos were recorded at 20 frames per second.

For underwater experiments, 1 ml MilliQ water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before experiment,
the pad was repeatedly brought into contact with the surface 10 times
to equilibriate the pad system. 5 force measurements were subsequently
performed on a fresh spot of the substrate and averaged for data analysis.
Experiments were repeated with 5 individual beetles for each type
of contact and substrate. In total, 30 beetles were tested.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup. Representative force data
and contact area of distal pad are shown in the plot, in which, the
shaded regions represent distinct piezo motion steps, negative force
values represent attraction and the minimum force peak during the
final retraction step is the adhesion force.}
\end{figure}

@@

For measurements in air, pull-off force was defined as the minimum
negative force during the final retraction step. For underwater measurements,
an additional correction was necessary. When the beetle was submerged
underwater, its contact line at the water surface shifted, which influenced
the force readout due to surface tension effects. This effect needed
to be canceled. So, a ``background'' force data was recorded, where
the submerged beetle makes no contact with the substrate. This background
data was then subtracted from a typical force data with substrate
contact to correct for the external surface tension effects. The pull-off
force was subsequently calculated from the minima as before.

@@

@@

Molecular weights of the secreted fluid mixtures extracted from an
Asian ladybird's leg, without and after immersion in water are compared
(Table \ref{tab:Molecular-distribution-of}). Except for two molecular
weights (406.8 g/mol and 331.6 g/mol), the chemical fingerprint remained
unchanged, indicating that the adhesion fluid was not washed away
underwater. Probable compounds in the fluid, corresponding to the
resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes.

@@

Adhesion force for the distal pad of ladybug beetle against glass
and PFOTS in air and underwater conditions are compared (Figure \ref{fig:Effect-of-contact}
and Table \ref{tab:Statistical-analysis}). In air, there is no significant
difference in the adhesion force between glass and PFOTS substrate
(p = 0.959). Underwater however, when there is no trapped bubble,
adhesion on a PFOTS surface is significantly larger than on glass
(p < 0.001). On PFOTS, there is no significant difference in the adhesion
force in air or underwater conditions. But on glass, adhesion in air
is significantly larger than underwater, either in the presence (p
= 0.002) or absence (p < 0.011) of the bubble. At the same, we see
that the presence of the bubble results in a higher adhesion force
than with no bubble (CLES = 0.84) on glass, although the difference
is not statistically significant (p = 0.07).

\begin{table}[H]
\noindent \begin{centering}
\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
\hline 
Fixed & A & B & p-value & CLES\tabularnewline
\hline 
\hline 
In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
\hline 
Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
\hline 
Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
\hline 
PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
\hline 
PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
\hline 
Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
\hline 
Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{Pairwise statistical comparison of single leg adhesion force of the
beetle for each contact type and substrate. The uncorrected p-values
and Common Language Effect Size (CLES) are obtained from post-hoc
pair-wise Student t-test between A and B while keeping the third parameter
fixed. p-values showing statistically significant difference between
A and B are in boldface. The condition for statistical significance
is based on the Bonferroni-corrected critical p-value of 0.008.\label{tab:Statistical-analysis}}
\end{table}
\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Single leg adhesion force measurements
of ladybug beetle (\emph{Coccinella septempuctata}) on glass and PFOTS
substrates in air and underwater conditions. Values represent peak
force of a distal pad pulled off from each substrate. Three types
of contact are seen in underwater experiments and are represented
separately: \textquotedblleft\emph{bubble}\textquotedblright , \textquotedblleft\emph{no
bubble}\textquotedblright{} and \textquotedblleft\emph{bad contact}\textquotedblright .
Stars represent theoretical predictions of adhesion force calculated
from the capillary bridge model, where hair diameter = 4 \textgreek{m}m,
pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water are assumed to be 24
mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

Apart from the three predicted contact types, we also observed an
additional fourth type of contact which sometimes occurs underwater,
labeled as ``\emph{bad contact}''. In this scenario, the ventral
view recordings show that the hairs don't appear to contact well with
the substrate, unlike the other three contact types. ``\emph{Bad
contact}'' shows no adhesion with either glass or PFOTS substrate.
While it's not completely clear why such a contact occurs, there can
be two possible reasons. First, the hairs could get bundled due to
a small air meniscus within the hairs, resulting in their disorientation.
Second, a thin water layer at the substrate interface might not be
drained out to allow the hairs to make contact with the substrate,
resulting in a loss of adhesion.

@@

We model the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$, as shown in figure \ref{fig:Model}. The hairs and the pad
are assumed to be perfectly rigid, for simplicity. The tip of each
hair has an adhesive fluid of volume, $V_{f}$, making contact with
the substrate. The fluid is pinned to the circumference of the hair
and forms a capillary bridge of height, $d$. Similar to our experiments,
we consider three types of contacts for the pad: 1) \emph{In air},
2) \emph{Underwater: no bubble} and 3) \emph{Underwater: bubble}.
In the third case, a bubble of volume, $V_{b}$, is trapped between
the hairs and pinned to the pad circumference.

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}
Let $V_{f}=\frac{4}{3}\pi s_{f}^{3}$ and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$,
where $s_{f}$ and $s_{b}$ are the radii of spheres with equivalent
volumes. Fluid and bubble radii are assumed to scale proportional
to their corresponding pinned contact diameter. We thus defined the
size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$ and $\phi_{b}=D_{p}/\left(2s_{b}\right)$
for the fluid and bubble respectively, to conveniently scale their
volumes relative to the hair and pad diameters they were pinned to.

@@

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure. Force versus distance for a single capillary
bridge is calculated by Surface Evolver simulations\cite{RN206},
(described in \ref{subsec:Simulation-Method}) and used to obtain
$F_{net}$ as a function of $d$ for each type of contact. The adhesion
force of the complete hairy pad system is then obtained from the minima
of $F_{net}$, where negative force values represent attraction.

We have considered $f_{air}$ and $f_{water}$ to be distinct terms
because the capillary force by the adhesive fluid will be different
in air and underwater due to its different contact angle and interfacial
tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations,
one can derive the following relation for the contact angle of the
adhesive fluid underwater:

@@

\subsubsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}

>>>>

\email{endlein01@mpip-mainz.mpg.de}

@@

\begin{document}
\begin{abstract}
Insects like beetles can stick to various surfaces using hairy pads
on their legs. It was previously shown that these pads can even attach
underwater, presumably due to an air bubble trapped around the pad.
However, the bubble's contribution to adhesion via capillary force
remained unclear. To investigate the role of the bubble, we measured\emph{
in-vivo} underwater adhesion of a ladybug's pad, in the presence and
absence of the trapped bubble and compare it with its adhesion in
air. Our experiments reveal that on a hydrophobic substrate, even
without a bubble, the pad can show adhesion underwater comparable
to that in air. On a hydrophilic substrate, underwater adhesion is
significantly reduced, with or without a trapped bubble. To explain
these results, we develop a simple theoretical model for the net adhesion
of a hairy pad due to capillary forces. Our results demonstrate that
the wetting properties of the adhesive fluid determines the insect's
adhesion in both air and underwater conditions.
\end{abstract}

@@

The question of how insects and other small animals can walk on smooth
surfaces against gravity has fascinated scientists for at least the
past three centuries \cite{RN198,RN59}. We now know that such animals
are able to adhere by using specialized organs on their feet called
adhesive pads. These adhesive pads exist in a variety of types depending
on the animal, but are generally categorized into: 1) ``smooth pads''
found in ants\cite{RN201}, stick insects \cite{RN182}, etc. and
2) ``hairy pads'' seen in flies \cite{RN155}, geckos \cite{RN202}
and others. The hairy pads show: 1) compliance to rough surfaces due
to their lower effective modulus, 2) angle dependent adhesion due
to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20},
which makes them suitable to adhere to most surfaces reversibly. Many
of these insects pads also secrete an adhesive fluid, as seen in flies
and ants \cite{RN201} (``wet adhesion''), while others such as
spiders and geckos rely on their dry hairy pads for attachment (``dry
adhesion''). In the ``wet adhesion'' case, fluid secretion can
enforce adhesion through surface tension and viscous forces \cite{RN71},
while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

@@

While most of the studies on insect adhesion are done under natural
conditions in air, insect attachment underwater has been relatively
unexplored. Typically, underwater adhesion is complicated to achieve
due to the difficulty in displacing the water layer and enable good
contact\cite{RN123}. Regardless, a study on leaf beetles\cite{RN87}
has revealed that they can in fact attach quite well to surfaces underwater.
Its hairy pad traps an air bubble underwater, which dewets the surface
on contact. It has been hypothesized that a combination of capillary
forces due the air bubble and hair secretions within the dewetted
area results in its adhesion underwater. However, a detailed investigation
of the bubble's contribution and necessity to adhere to different
surfaces is lacking. Geckos are also known to adhere underwater, where
its shear adhesion force on hydrophobic substrates are similar in
both air and underwater conditions. Interestingly, its adhesion on
a fluorinated substrate is even larger underwater than in air\cite{RN15}.
This has been partially explained by a thermodynamic work of adhesion
model, assuming full displacement of water at the interface, leading
to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalized picture of adhesion
for insects which use hairy pads and secrete a oily fluid for attachment.
First, we measured adhesion of a single constrained pad of a live
ladybug beetle in air and underwater conditions, both on smooth hydrophilic
and hydrophobic glass surfaces, with a microscopic observation of
the contact process. Second, we developed a simple theoretical model
considering capillary forces to predict the net adhesion force of
a hairy pad under different conditions. The case of underwater adhesion
was studied both in the presence and absence of a trapped bubble,
to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards
to understanding adhesion in other animals.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) were used for adhesion
tests. The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water\emph{ ad libitum}.

Each leg of the beetle has a pair of hairy pads covered with mostly
discoidal shaped setae, capable of strong adhesion. For the test,
we only allowed the distal-end pad to make contact. The beetle's leg
was constrained similar to the method described by Bullock et al \cite{RN19}.
A steel ball fixed with a piece of thick solder wire served as a rotatable
holder to fix the beetle and align its leg (Figure \ref{fig:Setup}).
The beetle was first anesthetized using CO\textsubscript{2} sublimating
from a piece of dry ice and then glued to the steel ball on its back.
Its front left leg was carefully fixed to the solder wire of the holder
using Blue-Tac. Its claws were fixed using epoxy glue to prevent any
wiggling. A small piece of non-sticky Teflon tape helped to keep its
other legs tucked close to the body and avoid their interference during
the adhesion test.

@@

The substrate wettability was characterized by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
\end{table}

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A 3 axis manual micro-manipulator
together with the rotatable steel ball allowed good alignment of the
beetle's foot to the substrate. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with cameras
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualized through
the substrate in total reflection mode by the ventral view camera.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronized using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before experiment,
the pad was repeatedly brought into contact with the surface 10 times
to equilibriate the pad system. 5 force measurements were subsequently
performed on a fresh spot of the substrate and averaged for data analysis.
Experiments were repeated with 5 individual beetles for each type
of contact and substrate. In total, 30 beetles were tested.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup. The recorded force data and
contact area of distal pad are shown in the plot, in which, the shaded
regions represent distinct piezo motion steps, negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force.}
\end{figure}

@@

A previous study on archanids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To confirm if even the beetle retains
its adhesive fluid underwater, we perform Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension effects. This effect needed to be canceled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS are rather similar; no significant differences are
detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
In contrast, underwater adhesion on PFOTS surface is significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
is observed both in the presence and absence of a trapped bubble.
In both cases, adhesion force reach similar values as in air. In contrast,
on glass, adhesion underwater is significantly reduced as compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). Underwater adhesion on glass tends to be slightly
higher in the presence of a bubble (CLES = 0.84). However, this difference
is small and not statistically significant (p = 0.07).

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two types of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textgreek{m}m,
pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

Apart from the three depicted contact types, we observed an additional
fourth type which occurred in roughly 25\% of our underwater experiments.
In this scenario, the ventral view recordings show that the hairs
did not appear to contact well with the substrate, unlike the other
three contact types. This ``bad contact'' scenario shows no adhesion
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes.

@@

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}
We model the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad are assumed
to be perfectly rigid, for simplicity. The tip of each hair has an
adhesive fluid of volume, $V_{f}$, making contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we consider three
types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

To characterize the adhesive fluid and bubble volume we define two
radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
are the radii of spheres with equivalent volumes. Fluid and bubble
radii are assumed to scale proportional to their corresponding pinned
contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
and $\phi_{b}=D_{p}/\left(2s_{b}\right)$ for the fluid and bubble
respectively, to conveniently scale their volumes relative to the
hair and pad diameters they were pinned to.

@@

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure (equation \ref{eq:f_bridge}). Force
versus distance for a single capillary bridge is calculated by Surface
Evolver simulations\cite{RN206}, (described in \ref{subsec:Simulation-Method})
and used to obtain $F_{net}$ as a function of $d$ for each type
of contact. The adhesion force of the complete hairy pad system is
then obtained from the minima of $F_{net}$, where negative force
values represent attraction.

We have considered $f_{air}$ and $f_{water}$ to be distinct terms
because the capillary force by the adhesive fluid will be different
in air and underwater due to its different contact angle and interfacial
tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations
for each case of fluid-air, fluid-water and water-air interface, one
can derive the following relation for the contact angle of the adhesive
fluid underwater:

@@

\subsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}

Forces due to a single pinned capillary liquid bridge in contact with
a substrate are obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
We see that, generally, the shape of the liquid meniscus determines
the strength of its adhesion force. High adhesion is seen for contact
angles less than $\sim$ 70\textdegree{} due to a net negative curvature
of the meniscus, while low adhesion is seen for contact angles greater
than $\sim$ 150\textdegree{} due to its net curvature being close
to zero. The Laplace pressure contribution to the net adhesion force
dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero.
